detrendr Meeting notes

### 2018-10-26 Notes/Gurobi_notes.Rmd
Meeting notes updated

Approximate objective: 
Define $\tilde{f}(x, \tau) = \sum_i \frac{1}{2*100\pi}log[cosh(100\pi x_i)] + (\tau - \frac{1}{2}) x_i$

min $\tilde{f}(y - \theta, \tau) + \tilde{f}(D\theta, 0.5)$

@@

```{r, cache = TRUE}
lambda <- 400/2
y <- spodNode$pid[1:400]
theta_g <- gurobi_trend(y, tau, 400, k)
D <- get_Dk(length(y), k)

@@

m2 <- microbenchmark(
lbfgs_sol <- lbfgs(obj, grad_obj, vars = phi0,  y=y, tau=tau, D=D, 
                lambda = lambda, invisible = 1),
trust_sol <- trust.optim(phi0, obj, grad_obj, hess_obj, 
                      method = "Sparse", 
                      control = list(report.level = 0), 
                      y=y, tau=tau, 
                      D=D, lambda=lambda),
times = 1
)

@@

knitr::kable(data.frame(method = c("LBFGS", "Trust Region"), 
                        time = summary(m2)$mean), digits = 1)
```

@@

```{r, cache = TRUE}
k <- 3
tau <- c(0.05, 0.5)
df <- spodNode
y <- df$pid[1:3600]
n <- length(y)
lambdaSeq <- c(5*n, 10*n, 11*n, 12*n, 13*n, 14*n, 15*n)

@@

```{r, cache = TRUE, message = FALSE}
nodes <- c("f", "g", "h")
plot_df <- data.frame(time = spodNode$time)
tau <- 0.05
for (node in nodes){
  pidCol <- paste(node, "SPOD.PID..V.", sep=".")
  spodNode <- spod[, c("time", pidCol)]
  names(spodNode)[2] <- c("pid")
  spodNode$pid <- as.numeric(scale(spodNode$pid, center = TRUE))
  theta_df <- get_windows(spodNode$pid, spodNode$time, k, tau,
                          43200, 3600, 600)
  theta_comb <- theta_df %>% 
    group_by(time) %>% 
    summarise(
      theta = mean(theta)
      )

>>>>

Approximate objective: 
Define $\hat{f}(x, \tau) = \sum_i \frac{1}{2*10^4\pi}log[cosh(10^4\pi x_i)] + (\tau - \frac{1}{2}) x_i$

min $\hat{f}(y - \theta, \tau) + \hat{f}(D\theta, 0.5)$

@@

## Compare times on n=200
```{r, cache = TRUE}
lambda <- 200/2
y <- spodNode$pid[1:200]
theta_g <- gurobi_trend(y, tau, 200, k)
D <- get_Dk(length(y), k)

@@

m2 <- microbenchmark(
  theta_g <- gurobi_trend(y, tau, 200, k),
  lbfgs_sol <- lbfgs(obj, grad_obj, vars = phi0,  y=y, tau=tau, D=D, 
                  lambda = lambda, invisible = 1),
  trust_sol <- trust.optim(phi0, obj, grad_obj, hess_obj, 
                        method = "Sparse", 
                        control = list(report.level = 0), 
                        y=y, tau=tau, 
                        D=D, lambda=lambda),
  times = 5
)

@@

knitr::kable(data.frame(method = c("Gurobi", "LBFGS", "Trust Region"), 
                        time = summary(m2)$mean), digits = 1)
```
## Compare results

@@

```{r, cache = TRUE}
k <- 3
tau <- c(0.05, 0.5)
df <- spodNode
y <- df$pid[1:3600]
n <- length(y)
lambdaSeq <- c(10*n, 12*n, 14*n, 16*n)

@@

```{r, cache = TRUE, message = FALSE}
nodes <- c("f", "g", "h")
plot_df <- data.frame(time = spodNode$time)
tau <- 0.05
for (node in nodes){
  pidCol <- paste(node, "SPOD.PID..V.", sep=".")
  spodNode <- spod[, c("time", pidCol)]
  names(spodNode)[2] <- c("pid")
  spodNode$pid <- as.numeric(scale(spodNode$pid, center = TRUE))
  theta_df <- get_windows(spodNode$pid, spodNode$time, k, tau,
                          spod_cv$lambda, 3600, 600)
  theta_comb <- theta_df %>% 
    group_by(time) %>% 
    summarise(
      theta = mean(theta)
      )
